---
title: "SI PROJECT 2"
author: "SHASHANK VIKRAM SINGH"
date: "22/10/2021"
output:
 
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Overview
The project aim is to analyze the ToothGrowth data in the R datasets package.

Load the necessary packages
```{r}
library(ggplot2)
library(tinytex)
library(datasets)
```

1. Load the ToothGrowth data 
```{r}
data(ToothGrowth)
str(ToothGrowth)

```
Summary of the data
```{r}
summary(ToothGrowth)
```
2.Basic summary of the data
```{r}
Supplement_mean = split(ToothGrowth$len, ToothGrowth$supp)
sapply(Supplement_mean, mean)
```
Graph
```{r}
ggplot(aes(x=supp, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=supp))+ 
        xlab("Supplement Type") +ylab("Tooth length") 
```
3.  compare growth of tooth by supplement dose
```{r}
unique(ToothGrowth$dose)
```
There are 3 dose groups: 0.5, 1, and 2
 Tooth length vs Dose
```{r}
g <- ggplot(aes(x = factor(dose), y = len), data = ToothGrowth) + 
    geom_boxplot(aes(fill = factor(dose)))
g <- g + labs(title="Tooth Lenghtvs dosage")
print(g)
```
T-test for dose 0.5 mg:
```{r}
t.test(len ~ supp, ToothGrowth[ToothGrowth$dose == .5, ])
```
T-test for dose 1 mg:
```{r}
t.test(len ~ supp, ToothGrowth[ToothGrowth$dose == 1, ])
```
T-test for dose 2 mg:
```{r}
t.test(len ~ supp, ToothGrowth[ToothGrowth$dose == 2, ])
```

Due to small P value we can reject null hypothesis and conclude that supliment has no effect on teath growth.



